Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-02 papers/ms.tex
add plot_koikeplerlc
ditto to ms
compile paper

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia
  are yielding a refined view of stellar clusters during the
  first hundred million years of their lives.
  Here we present an analysis of a group of $38 \pm 6$ million year old stars
  in the Cepheus-Hercules region, hereafter the Cep-Her complex.
  This group of stars includes four previously known Kepler Objects of
  Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
	Kepler-1627 is a previously validated young planet
	in a component of the Cep-Her complex called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.
	Here we focus on the latter three systems, which are in other sub-components
	of the complex (RSG5 and CH-2).
	Based on kinematic evidence from Gaia, stellar rotation periods from TESS, and spectroscopy,
	these three systems are also $38 \pm 6$ million years old.
	Based on the transit shapes and high resolution imaging, we
	statistically validate that they are all most likely planets (false positive probabilities of $6\times10^{-9}$,
	$5\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368, and
	KOI-7913 respectively).
	Supplemented by Gaia and TESS, the main Kepler mission is now contributing to the
	census of young close-in planets, and Kepler-1643 and KOI-7913 are the first
	empirical demonstration that mini-Neptunes with sizes of $\approx$2 Earth radii
	exist at ages of roughly 40 million years.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    $\delta$\,Lyr cluster.} 
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
		\label{fig:age}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3a.png}
			\includegraphics[width=0.5\textwidth]{f3b.png}
		}

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3c.png}
			\includegraphics[width=0.5\textwidth]{f3d.png}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf planets.} 
		\label{fig:planets}
	}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty. STAR, SQUARE, DIAMOND.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

>>>>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia
  are yielding a refined view of stellar clusters during the
  first hundred million years of their lives.
  Here we present an analysis of a group of $38 \pm 6$ million year old stars
  spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$), hereafter the Cep-Her complex.
  This group of stars includes four previously known Kepler Objects of
  Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a component of the Cep-Her
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the latter three
  systems, which are in other sub-components of the complex (RSG-5 and
  CH-2).  Based on kinematic evidence from Gaia, stellar rotation
  periods from TESS, and spectroscopy, these three systems are also
  $38 \pm 6$ million years old.  Based on the transit shapes and high
  resolution imaging, we statistically validate that they are all most
  likely planets (false positive probabilities of $6\times10^{-9}$,
  $5\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively).  Supplemented by Gaia and TESS, the main
  Kepler mission is now contributing to the census of young close-in
  planets, and Kepler-1643 and KOI-7913 are the first empirical
  demonstration that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of roughly 40 million years.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    complex.} 
    Sub-clusters include the $\delta$ Lyr cluster, RSG-5, and the
    worryingly diffuse ``CH-2''.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{TEMP_f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
    The top row shows CAMDs.  Left shows CH-2, right shows RSG-5.
    The bottom left shows gyro.
    The bottom right shows lithium (and is a {\bf place-holder}).  (Somewhere we will have
    H-alpha?).
		\label{fig:age}
	}
\end{figure*}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.99\textwidth]{f3e.pdf}
		}

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3a.pdf}
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
		}

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
			\includegraphics[width=0.5\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Raw and processed light curves for the objects of
    interest.} Top: raw.  Bottom: processed.
    There increases scatter during transit is likely due to starspot
    crossing events.
		\label{fig:planets}
	}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    %    namelist = ['Kepler-1627 A', 'KOI-7368', 'KOI-7913 A', 'KOI-7913 B', 'Kepler-1643']
    %    markers = ['P', 'v', 'X', 'X', 's']
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty. Kepler-1627 (+), KOI-7368 (down-triangle),
    KOI-7913 (X), Kepler-1643 (diamond).  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2022
		Feb 27).
		\label{fig:rp_period_age}
	}
\end{figure*}
